---
title: "athal_bioclim"
output: html_document
---

#Searching for some sort of association between CNS structure and bioclim data

- code continuously along phylogeny and pca plot
- start with PCA

Code_block: PCA
- load in pca table
- Figure out how to code continuously

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

merged_df = read.table( file = "/Users/alanyocca/Documents/01_athal_cns/pca_data_table.txt",row.names = NULL,sep = "\t", header = T)

#change terminology
merged_df$Tag = gsub("Missing","PAV",merged_df$Tag)
merged_df$Tag = gsub("Moved","PosV",merged_df$Tag)

#add common names
adp_meta_table = read.table(file = "/Users/alanyocca/Documents/01_athal_cns/final_gen_eco_cn_id.txt",header = T, sep = "\t", stringsAsFactors = F)

#add latitude, longitude
srr_lat_long = read.table(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/srr_lat_long.txt",header = F,row.names = NULL,sep = "\t")

colnames(srr_lat_long) = c("SRR","Lat","Long")
srr_lat_long$SRR = gsub("_.*","",srr_lat_long$SRR)

comb_lat_long_meta = merge(srr_lat_long,adp_meta_table)

Common_Name_vect = vector()
Lat = vector()
Long = vector()
Ecotype = vector()
Geo = vector()
for (i in 1:nrow(comb_lat_long_meta)) {
  indicies = which(grepl(comb_lat_long_meta$SRR[i],merged_df$Accession))
  Common_Name_vect[indicies] = comb_lat_long_meta$Common_Name[i]
  Lat[indicies] = comb_lat_long_meta$Lat[i]
  Long[indicies] = comb_lat_long_meta$Long[i]
  Ecotype[indicies] = comb_lat_long_meta$ecotype[i]
  Geo[indicies] = comb_lat_long_meta$geo_loc_name[i]
}

merged_df = cbind(merged_df,Common_Name_vect,Lat,Long,Ecotype,Geo)

#add continuous variables, playing around with colors
#just play around
random_continuous = runif(nrow(merged_df),min = 0, max = 1)
merged_df = cbind(merged_df,random_continuous)

#sapply(merged_df,class)
pca_plot = merged_df[which(merged_df$Tag == "PAV"),] %>% 
  ggplot(aes(x = PC1 , y = PC2, color = random_continuous)) +
  geom_point() +
  scale_colour_gradient(low = "#132B43", high = "#56B1F7")
pca_plot
# nice
# going to be a little more difficult for tip labels because will scale manually....
# welp have precip data downloaded
# going to be difficult to assign, no?
# perhaps write my own function for that, simple
# just find lat/long interval it falls between, slide along

#save file, here believe we added PCA to our adp meta table
merged_df = merged_df[,1:(ncol(merged_df) - 1)]
colnames(merged_df)[6] = "Common_Name"


write.table(merged_df,file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/adp_pca_table.txt",sep = "\t",quote = F,row.names = F)
 
```

Code_block: Retrieve BioClim
- try and get bioclim data for given lat / long

```{r}
#rm(list=ls(all=TRUE))
#install.packages("raster")
#install.packages("sp")
library(raster)
library(sp)

r <- getData("worldclim",var="bio",res=10)
r <- r[[c(1,12)]]
names(r) <- c("Temp","Prec")

lats <- c(9.093028 , 9.396111, 9.161417)
lons <- c(-11.7235, -11.72975, -11.709417) 

coords <- data.frame(x=lons,y=lats)

points <- SpatialPoints(coords, proj4string = r@crs)

values <- extract(r,points)

df <- cbind.data.frame(coordinates(points),values)
df
```

Code_block: BioClim_test
- add bioclim into meta_data table:
  - PCAs, Accession, Common name, lat/long, and 19 Bioclim vars
- just getting code to work here
- yea you shouldn't run this code block
```{r}
rm(list=ls(all=TRUE))
library(raster)
#library(sp)

pca_table = read.table(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/adp_pca_table.txt",sep = "\t",header = T,row.names = NULL)

#gots some lats and longs, add bioclim to this table
#?getData
r <- getData("worldclim",var="bio",res=2.5)

#what if I just search each lat and long separately?
#because want higher res hopefully less NA
lat_long_pairs = unique(pca_table[,c('Lat','Long')])

#?getData
#r <- getData("worldclim",var="bio",res=0.5,lat=lat_long_pairs[2,1],lon=lat_long_pairs[2,2])

r <- r[[1]]
names(r) = "Temp"
names(r) <- c("Temp",
              "Diurnal_Range",
              "Isotherm",
              "Tmp_szn",
              "Max_temp",
              "Min_temp",
              "Tmp_range",
              "Tmp_wet",
              "Tmp_dry",
              "Tmp_warm",
              "Tmp_cold",
              "Precip",
              "Prec_wetm",
              "Prec_drym",
              "Prec_szn",
              "Prec_wetq",
              "Prec_dryq",
              "Prec_warmq",
              "Prec_coldq")

coords = data.frame(pca_table$Long,pca_table$Lat)
#?SpatialPoints
points <- SpatialPoints(coords, proj4string = r@crs)
#?extract
values <- extract(r,coords)

#crop raster file first
limits = extent(-74,-73,40.4,41)
#limits = extent(46.9,47.1,15.4,15.6)
r_crop = crop(r,limits)

sampled = apply(X = coords, MARGIN = 1, FUN = function(coords) r_crop@data@values[which.min(replace(distanceFromPoints(r_crop, coords), is.na(r_crop), NA))])

#values(r,1)
#r@layers[[1]]

#r_tmp <- raster(ncol=10,nrow=10, xmn=0, xmx=10, ymn=0,ymx=10)
#r_tmp[] <- 1:10
#r_tmp[sample(1:ncell(r_tmp), size = 25)] <- NA

#nl = nearestLand(points, r)

#install.packages("remotes")
#remotes::install_github("SEEG-Oxford/seegSDM")
#library(seegSDM)

#nl = nearestLand(coords, r,max_distance = 1000000)
#??nearestLand()

#crop raster file first
limits = extent(40.4,41,73,74)

r_crop = crop(r,limits)

#try to loop through the layers
dist <- distance(r)  
# you can also set a maximum distance: dist[dist > maxdist] <- NA
direct <- direction(r_crop, from=FALSE)

# NA raster
rna <- is.na(r_crop@layers[[1]]) # returns NA raster

# store coordinates in new raster: https://stackoverflow.com/a/35592230/3752258 
na.x <- init(rna, 'x')
na.y <- init(rna, 'y')

# calculate coordinates of the nearest Non-NA pixel
# assume that we have a orthogonal, projected CRS, so we can use (Pythagorean) calculations
co.x <- na.x + dist * sin(direct)
co.y <- na.y + dist * cos(direct)

# matrix with point coordinates of nearest non-NA pixel
co <- cbind(co.x[], co.y[]) 

# extract values of nearest non-NA cell with coordinates co
NAVals <- raster::extract(r, co, method='simple') 
r.NAVals <- rna # initiate new raster
r.NAVals[] <- NAVals # store values in raster

# cover nearest non-NA value at NA locations of original raster
r.filled <- cover(x=r, y= r.NAVals)

sampled <- raster::extract(x = r.filled, y = xy)



bioclim <- cbind.data.frame(coordinates(points),values)
colnames(bioclim)[1:2] = c("Lat","Long")

bioclim_meta = merge(bioclim,pca_table)



```

Code_block: Add_BioClim
- add bioclim to meta_data table

```{r}
rm(list=ls(all=TRUE))
library(raster)
#library(sp)
#loading raster automatically loads sp

pca_table = read.table(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/adp_pca_table.txt",sep = "\t",header = T,row.names = NULL)

#gots some lats and longs, add bioclim to this table
#?getData
r <- getData("worldclim",var="bio",res=2.5)

names(r) <- c("Temp",
              "Diurnal_Range",
              "Isotherm",
              "Tmp_szn",
              "Max_temp",
              "Min_temp",
              "Tmp_range",
              "Tmp_wet",
              "Tmp_dry",
              "Tmp_warm",
              "Tmp_cold",
              "Precip",
              "Prec_wetm",
              "Prec_drym",
              "Prec_szn",
              "Prec_wetq",
              "Prec_dryq",
              "Prec_warmq",
              "Prec_coldq")

coords = data.frame(pca_table$Long,pca_table$Lat)
#?SpatialPoints
points <- SpatialPoints(coords, proj4string = r@crs)
#?extract
values <- extract(r,coords)

bioclim <- cbind.data.frame(coordinates(points),values)
colnames(bioclim)[1:2] = c("Long","Lat")

colnames(bioclim)
colnames(pca_table)
head(bioclim[,1:2])
head(pca_table[,c("Lat","Long")])

bioclim_meta = unique(merge(bioclim,pca_table,by=c("Long","Lat")))

write.table(bioclim_meta,file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/bioclim_pca.txt",col.names = T,row.names = F,sep = "\t",quote = F)
```

Code_block: BioClim_PCA

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

##atac_colour = "#00B0F6"
#gene_colour = "#00BF7D"
#cns_colour = "#A3A500"
#peak_colour = "#E76BF3"
#?col2rgb
pav_pca = bioclim_pca_tidy[which(bioclim_pca_tidy$Variable == "Temp" & bioclim_pca_tidy$Tag == "PAV"),] %>% 
  ggplot(aes(x=PC1,y=PC2,color=Value)) +
  geom_point(size = 7) +
#  facet_wrap(~Variable) +
  scale_colour_gradient(low = "gold", high = "black") +
  theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
  theme_minimal()
#  scale_colour_gradient(low = "#132B43", high = "#56B1F7")
pav_pca
#i = "Temp"

#rename values to temperature and adjust / 10
bioclim_pca_tidy = bioclim_pca_tidy %>% 
  mutate('*~degree*C*' = Value / 10)
tmp_pca = bioclim_pca_tidy[which(bioclim_pca_tidy$Variable == i & bioclim_pca_tidy$Tag == "PAV"),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=Value)) +
  geom_point(size = 7) +
#  facet_wrap(~Variable) +
  scale_colour_gradient(low = "gold", high = "black") +
  theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
  theme_minimal()
#  tmp_pca
# break
  pdf(file = paste0(bioclim_dir,"pca_pav_",i,".pdf"))
    plot(tmp_pca)
    dev.off()
  rm(tmp_pca)




for (i in unique(bioclim_pca_tidy$Variable)) {
  print(i)
  tmp_pca = bioclim_pca_tidy[which(bioclim_pca_tidy$Variable == i & bioclim_pca_tidy$Tag == "PAV"),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=Value)) +
  geom_point(size = 7) +
#  facet_wrap(~Variable) +
  scale_colour_gradient(low = "gold", high = "black") +
  theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
  theme_minimal()
#  tmp_pca
# break
  pdf(file = paste0(bioclim_dir,"pca_pav_",i,".pdf"))
    plot(tmp_pca)
    dev.off()
  rm(tmp_pca)
}
for (i in unique(bioclim_pca_tidy$Variable)) {
  print(i)
  tmp_pca = bioclim_pca_tidy[which(bioclim_pca_tidy$Variable == i & bioclim_pca_tidy$Tag == "PosV"),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=Value)) +
    geom_point() +
    scale_colour_gradient(low = "blue", high = "red") +
    ggtitle(paste0("PAV PCA ", i))
#  tmp_pca
# break
  pdf(file = paste0(bioclim_dir,"pca_posv_",i,".pdf"))
    plot(tmp_pca)
    dev.off()
  rm(tmp_pca)
}


moved_to_missing_plot <- ggplot(moved_to_missing, aes(PC2, PC1)) +
  geom_point(aes(colour = Group), size = 3) +
  theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
  labs(fill="Admixture Group") 
  
  
  
#names(r) <- c("Temp",
#              "Diurnal_Range",
#              "Isotherm",
#              "Tmp_szn",
#              "Max_temp",
#              "Min_temp",
#              "Tmp_range",
#              "Tmp_wet",
#              "Tmp_dry",
#              "Tmp_warm",
#              "Tmp_cold",
#              "Precip",
#              "Prec_wetm",
#              "Prec_drym",
#              "Prec_szn",
#              "Prec_wetq",
#              "Prec_dryq",
#              "Prec_warmq",
#              "Prec_coldq")
```



above code is messy, lets get a function where we can control the bioclim variable and legend label, therefore also title, pav/posv

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

#bioclim_pca_tidy = bioclim_pca_tidy %>% 
#  mutate('*~degree*C*' = Value / 10)

pca_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T,code) {
  df = df %>% 
    mutate(units = unit_adj_function(Value))
  
  pca_fig = df[which(df$Variable == variable & df$Tag == tag),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=units)) +
    geom_point(size = 2) +
    scale_colour_gradient(low = "gold", high = "black", name = units) +
    theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
    theme_minimal() +
    labs(title = paste0(code, ".) ",tag))
#    geom_text(label = code, aes(x = -Inf, y = Inf, hjust = 0, vjust = 1 ))
  
  if (save == T) {
    pdf(file = paste0(dir,"/pca_",tag,"_",variable,".pdf"))
      plot(pca_fig)
      dev.off()
  }
  else {
    return((pca_fig))
  }
}

div_ten = function(x) {
  tmp = x / 10
  return(tmp)
}
none = function(x) {
  return(x)
}

pca_pav_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = F,code = "A")
pca_posv_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = F,code = "B")
pca_pav_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = F,code = "C")
pca_posv_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = 'mm',variable = "Precip", save = F,code = "D")


library(gridExtra)

pdf(file = paste0(bioclim_dir,"/pca_pav_posv_temp_prec.pdf"))
  grid.arrange(pca_pav_tmp,pca_posv_tmp, pca_pav_prec,pca_posv_prec,ncol = 2)
  dev.off()
```

Make a violin plot comparing the environmental variables of two clusters

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

#bioclim_pca_tidy = bioclim_pca_tidy %>% 
#  mutate('*~degree*C*' = Value / 10)

pca_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T,code) {
  df = df %>% 
    mutate(units = unit_adj_function(Value))
  
  pca_fig = df[which(df$Variable == variable & df$Tag == tag),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=units)) +
    geom_point(size = 2) +
    scale_colour_gradient(low = "gold", high = "black", name = units) +
    theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
    theme_minimal() +
    labs(title = paste0(code, ".) ",tag))
#    geom_text(label = code, aes(x = -Inf, y = Inf, hjust = 0, vjust = 1 ))
  
  if (save == T) {
    pdf(file = paste0(dir,"/pca_",tag,"_",variable,".pdf"))
      plot(pca_fig)
      dev.off()
  }
  else {
    return((pca_fig))
  }
}

div_ten = function(x) {
  tmp = x / 10
  return(tmp)
}
none = function(x) {
  return(x)
}

pca_posv_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = '\u00b0C',variable = "Temp",save = F,code = "A")
pca_posv_tmp

#first cluster PC2 > 2, PC1 < 10
bioclim_posv_pca = bioclim_pca_tidy[which(bioclim_pca_tidy$Tag == "PosV"),]
cluster_one = bioclim_posv_pca[(bioclim_posv_pca$PC1 < 10) & (bioclim_posv_pca$PC2 > 2),]
#length(unique(cluster_one$Accession))

cluster_two_accessions = setdiff(bioclim_posv_pca$Accession, cluster_one$Accession)
cluster_two = bioclim_posv_pca[which(bioclim_posv_pca$Accession %in% cluster_two_accessions),]

#nice, now get environmental variables into same dataframe and just tag with cluster
bioclim_posv_pca_cluster = bioclim_posv_pca %>%
  mutate("Cluster" = ifelse(Accession %in% cluster_one$Accession,
                            "Cluster_one","Cluster_two"))

#nice now violin plot for variable used in paper
temp_clust_plot = bioclim_posv_pca_cluster[which(bioclim_posv_pca_cluster$Variable == "Temp"),] %>% 
  ggplot(aes(x = Cluster, y = Value)) +
  geom_violin()
temp_clust_plot

prec_clust_plot = bioclim_posv_pca_cluster[which(bioclim_posv_pca_cluster$Variable == "Precip"),] %>% 
  ggplot(aes(x = Cluster, y = Value)) +
  geom_violin()
prec_clust_plot
```

Code_block: Bioclim_violin
- violin plots between clusters matching pca plots
- for now, manual curation of clusters
```{r}
#make function to:
#extract tag,
#extract variable
#add column designating cluster
#create violin plot with matching specs as pca plots
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)
library(ggrepel)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

#bioclim_pca_tidy = bioclim_pca_tidy %>% 
#  mutate('*~degree*C*' = Value / 10)

pca_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T,code) {
  df = df %>% 
    mutate(units = unit_adj_function(Value))
  
  pca_fig = df[which(df$Variable == variable & df$Tag == tag),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=units)) +
    geom_point(size = 2) +
    scale_colour_gradient(low = "gold", high = "black", name = units) +
    theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
    theme_minimal() +
    labs(title = paste0(code, ".) ",tag))
#    geom_text(label = code, aes(x = -Inf, y = Inf, hjust = 0, vjust = 1 ))
  
  if (save == T) {
    pdf(file = paste0(dir,"/pca_",tag,"_",variable,".pdf"))
      plot(pca_fig)
      dev.off()
  }
  else {
    return((pca_fig))
  }
}

div_ten = function(x) {
  tmp = x / 10
  return(tmp)
}
none = function(x) {
  return(x)
}

violin_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T, 
                            PC1_cutoff_lower = -9999999,
                            PC1_cutoff_upper = 999999, 
                            PC2_cutoff_lower = -999999, 
                            PC2_cutoff_upper = 999999) {

  df = df[which(df$Tag == tag),] %>% 
    mutate(units = unit_adj_function(Value))
 
  df = df[which(df$Variable == variable),]
  
  cluster_one = df[(df$PC1 < PC1_cutoff_upper) & 
                    (df$PC1 > PC1_cutoff_lower) & 
                    (df$PC2 < PC2_cutoff_upper) & 
                    (df$PC2 > PC2_cutoff_lower),]
  
  df = df %>% 
    mutate("Cluster" = ifelse(df$Accession %in% cluster_one$Accession,
                              "Upper Cluster",
                              "Lower Cluster"))
  df = df %>% 
   mutate(Avg_units = ifelse(Cluster == "Upper Cluster",
                            mean(df[which(df$Cluster == 
                              "Upper Cluster"),which(colnames(df) == "units")]),
                            mean(df[which(df$Cluster == 
                              "Lower Cluster"),which(colnames(df) == "units")])))
  
  violin = df %>% 
    ggplot(aes(x=Cluster,y=units)) +
    geom_violin(aes(fill = Avg_units)) +
    geom_point(aes(fill = units), size = 2, shape = 21, position = position_jitter(height = .2, width = .2)) +
    scale_fill_gradient(low = "gold", high = "black", 
                limits = c(min(df$units),max(df$units)),
                name = units) +
    theme(legend.text=element_text(size=25),
      legend.title = element_text(size = 25),
      axis.text=element_text(size=25), 
      axis.title.x = element_text(size=25),
      axis.title.y = element_text(size=25),
      title = element_text(size=25)) +  
    scale_y_continuous(name = variable) +
    theme_minimal() 
#    labs(title = tag)

  if (save == T) {
    pdf(file = paste0(dir,"/violin_",tag,"_",variable,".pdf"))
      plot(violin)
      dev.off()
  }
  else {
    return((violin))
  }
}


pca_pav_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = F,code = "A")
violin_pav_tmp = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = F, PC1_cutoff_upper = 0, PC2_cutoff_lower = 0)

pca_posv_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = F,code = "B")
violin_posv_tmp = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = F,PC1_cutoff_upper = 10, PC2_cutoff_lower = 2)

pca_pav_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = F,code = "C")
violin_pav_prec = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = F,PC1_cutoff_upper = 0, PC2_cutoff_lower = 0)

pca_posv_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = 'mm',variable = "Precip", save = F,code = "D")
violin_posv_prec = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = 'mm',variable = "Precip", save = F,PC1_cutoff_upper = 10, PC2_cutoff_lower = 2)

library(gridExtra)

#pdf(file = paste0(bioclim_dir,"/pca_violin_pav_posv_temp_prec.pdf"))
#  grid.arrange(pca_pav_tmp,violin_pav_tmp,
#               pca_posv_tmp,violin_posv_tmp, 
#               pca_pav_prec,violin_pav_prec,
#               pca_posv_prec,violin_posv_prec,ncol = 2)
#  dev.off()

#two separate graphs to split across page?
pdf(file = paste0(bioclim_dir,"/pca_violin_pav_posv_temp.pdf"))
  grid.arrange(pca_pav_tmp,violin_pav_tmp,
               pca_posv_tmp,violin_posv_tmp, 
               ncol = 2)
  dev.off()

pdf(file = paste0(bioclim_dir,"/pca_violin_pav_posv_prec.pdf"))
  grid.arrange(pca_pav_prec,violin_pav_prec,
               pca_posv_prec,violin_posv_prec,ncol = 2)
  dev.off()


```


Testing code
```{r}

#create bioclim_pca_tidy object, messing around with getting labels so can select accessions
#pca_posv_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = T,code = "B")

bioclim_pca_tidy = bioclim_pca_tidy %>% 
  mutate(units = unit_adj_function(Value))
tag = "PAV"
tmp = bioclim_pca_tidy[which(bioclim_pca_tidy$Variable == variable & bioclim_pca_tidy$Tag == tag),]


pca_fig = tmp %>% 
  ggplot(aes(x=PC1 , y=PC2, color=units, label = Common_Name)) +
  geom_text_repel() +
  geom_point(size = 2) +
  scale_colour_gradient(low = "gold", high = "black", name = units) +
  theme(legend.text=element_text(size=25),
      legend.title = element_text(size = 25),
      axis.text=element_text(size=25),
      axis.title.x = element_text(size=25),
      axis.title.y = element_text(size=25),
      title = element_text(size=25)) +
  theme_minimal() +
  labs(title = paste0(code, ".) ",tag))
pca_fig

#save
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//temp_posv_pca.pdf", height = 4.2, width = 6.2)
  pca_fig
  dev.off()
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//temp_pav_pca.pdf", height = 4.2, width = 6.2)
  pca_fig
  dev.off()


#a

###
###
###
df = df[which(df$Tag == tag),] %>% 
    mutate(units = unit_adj_function(Value))
  
  cluster_one = df[(df$PC1 < PC1_cutoff_upper) & 
                    (df$PC1 > PC1_cutoff_lower) & 
                    (df$PC2 < PC2_cutoff_upper) & 
                    (df$PC2 > PC1_cutoff_lower),]
  
  df = df %>% 
    mutate("Cluster" = ifelse(df$Accession %in% cluster_one$Accession,
                              "Cluster_one",
                              "Cluster_two"))
  
none = function(variables) {
  return(variables)
}
div_ten = function(x) {
  tmp = x / 10
  return(tmp)
}
temp_posv_df = bioclim_pca_tidy[which(bioclim_pca_tidy$Tag == "PAV"),] %>% 
  mutate(units = none(Value))

violin_pav_prec = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = F,PC1_cutoff_upper = 0, PC2_cutoff_lower = 0)

#PC1 < 10) & (bioclim_posv_pca$PC2 > 2),]
PC1_cutoff_upper = 0
PC1_cutoff_lower = -999999
PC2_cutoff_upper = 999999
PC2_cutoff_lower = 0

cluster_one = temp_posv_df[(temp_posv_df$PC1 < PC1_cutoff_upper) & 
                    (temp_posv_df$PC1 > PC1_cutoff_lower) & 
                    (temp_posv_df$PC2 < PC2_cutoff_upper) & 
                    (temp_posv_df$PC2 > PC2_cutoff_lower),]
#length(unique(cluster_one$Accession))
temp_posv_df = temp_posv_df[which(temp_posv_df$Variable == "Precip"),]
temp_posv_df = temp_posv_df %>% 
    mutate("Cluster" = ifelse(temp_posv_df$Accession %in% cluster_one$Accession,
                              "Upper Cluster",
                              "Lower Cluster"))
temp_posv_df = temp_posv_df %>% 
  mutate(Avg_units = ifelse(Cluster == "Cluster_one",
                            mean(temp_posv_df[which(temp_posv_df$Cluster == 
                                              "Upper Cluster"),which(colnames(temp_posv_df) == "units")]),
                            mean(temp_posv_df[which(temp_posv_df$Cluster == 
                                              "Lower Cluster"),which(colnames(temp_posv_df) == "units")])))

#mean(temp_posv_df[which(temp_posv_df$Cluster == "Cluster_two"),which(colnames(temp_posv_df) == "Value")])
#tmp = temp_posv_df[which(temp_posv_df$Cluster == "Cluster_two"),which(colnames(temp_posv_df) == "Value")]
#mean(tmp$Value)
ggplot(aes(x=PC1,y=PC2,color=units)) +
    geom_point(size = 2) +
    scale_colour_gradient(low = "gold", high = "black", name = units) 
units = 'mm'
variable = "Precip"

violin = temp_posv_df %>% 
  ggplot(aes(x=Cluster,y=units)) +
  geom_violin(aes(fill = Avg_units)) +
  geom_point(aes(fill = units), size = 2, shape = 21, position = position_jitter(height = .2, width = .2)) +
#  scale_color_gradient(low = "gold", high = "black", 
#                limits = c(min(temp_posv_df$units),max(temp_posv_df$units))) +
  scale_fill_gradient(low = "gold", high = "black", 
                limits = c(min(temp_posv_df$units),max(temp_posv_df$units)),
                name = units) +
  theme(legend.text=element_text(size=25),
    legend.title = element_text(size = 25),
    axis.text=element_text(size=25), 
    axis.title.x = element_text(size=25),
    axis.title.y = element_text(size=25),
    title = element_text(size=25)) +  
  scale_y_continuous(name = variable) +
  theme_minimal()
#    labs(title = paste0(code, ".) ",tag))
violin    
  
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/tmp_violin.pdf")
  violin
  dev.off()
    
```


Combine using multipanel fig

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

#bioclim_pca_tidy = bioclim_pca_tidy %>% 
#  mutate('*~degree*C*' = Value / 10)

pca_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T,code) {
  df = df %>% 
    mutate(units = unit_adj_function(Value))
  
  pca_fig = df[which(df$Variable == variable & df$Tag == tag),] %>% 
    ggplot(aes(x=PC1,y=PC2,color=units)) +
    geom_point(size = 2) +
    scale_colour_gradient(low = "gold", high = "black", name = units) +
    labs(title = tag) +
    theme(plot.title = element_text(size = 12, hjust = 0.5),
        legend.text = element_text(size=12),
        legend.title = element_text(size = 12),
        axis.text = element_text(size=12),
        axis.title.x = element_text(size=12),
        axis.title.y = element_text(size=12)) +
    theme_minimal()
#    geom_text(label = code, aes(x = -Inf, y = Inf, hjust = 0, vjust = 1 ))
  
  if (save == T) {
    pdf(file = paste0(dir,"/pca_",tag,"_",variable,".pdf"), height = 2, width = 3)
      plot(pca_fig)
      dev.off()
  }
  else {
    return((pca_fig))
  }
}

div_ten = function(x) {
  tmp = x / 10
  return(tmp)
}
none = function(x) {
  return(x)
}

violin_bioclim_plot = function(df,dir,variable,tag,units,
                            unit_adj_function,save = T, 
                            PC1_cutoff_lower = -9999999,
                            PC1_cutoff_upper = 999999, 
                            PC2_cutoff_lower = -999999, 
                            PC2_cutoff_upper = 999999) {

  df = df[which(df$Tag == tag),] %>% 
    mutate(units = unit_adj_function(Value))
 
  df = df[which(df$Variable == variable),]
  
  cluster_one = df[(df$PC1 < PC1_cutoff_upper) & 
                    (df$PC1 > PC1_cutoff_lower) & 
                    (df$PC2 < PC2_cutoff_upper) & 
                    (df$PC2 > PC2_cutoff_lower),]
  
  df = df %>% 
    mutate("Cluster" = ifelse(df$Accession %in% cluster_one$Accession,
                              "Upper Cluster",
                              "Lower Cluster"))
  df = df %>% 
   mutate(Avg_units = ifelse(Cluster == "Upper Cluster",
                            mean(df[which(df$Cluster == 
                              "Upper Cluster"),which(colnames(df) == "units")]),
                            mean(df[which(df$Cluster == 
                              "Lower Cluster"),which(colnames(df) == "units")])))
  
  violin = df %>% 
    ggplot(aes(x=Cluster,y=units)) +
    geom_violin(aes(fill = Avg_units)) +
    geom_point(aes(fill = units), size = 2, shape = 21, position = position_jitter(height = .2, width = .2)) +
    scale_fill_gradient(low = "gold", high = "black", 
                limits = c(min(df$units),max(df$units)),
                name = units) +
    labs(title = tag) +
    theme(legend.text=element_text(size=12),
      legend.title = element_text(size = 12),
      axis.text=element_text(size=12), 
      axis.title.x = element_text(size=12),
      axis.title.y = element_text(size=12),
      title = element_text(size=12)) +  
    scale_y_continuous(name = variable) +
    theme_minimal() 
#    labs(title = tag)

  if (save == T) {
    pdf(file = paste0(dir,"/violin_",tag,"_",variable,".pdf"), height = 2, width = 3)
      plot(violin)
      dev.off()
  }
  else {
    return((violin))
  }
}


pca_pav_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = T,code = "A")
#save separately, mess around with sizing

#pdf(file = paste0(bioclim_dir,"tmp_pca.pdf"), width = 3, height = 2)
#pca_pav_tmp
#dev.off()

violin_pav_tmp = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = T, PC1_cutoff_upper = 0, PC2_cutoff_lower = 0)

#pdf(file = paste0(bioclim_dir,"tmp_violin.pdf"), width = 3, height = 2)
#violin_pav_tmp
#dev.off()
#
#
#
#
#

pca_posv_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = T,code = "B")
violin_posv_tmp = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp", save = T,PC1_cutoff_upper = 10, PC2_cutoff_lower = 2)

pca_pav_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = T,code = "C")
violin_pav_prec = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PAV",units = 'mm',unit_adj_function = none,variable = "Precip",save = T,PC1_cutoff_upper = 0, PC2_cutoff_lower = 0)

pca_posv_prec = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = 'mm',variable = "Precip", save = T,code = "D")
violin_posv_prec = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "PosV",unit_adj_function = none,units = 'mm',variable = "Precip", save = T,PC1_cutoff_upper = 10, PC2_cutoff_lower = 2)


```

```{r}
library(multipanelfigure)

figure <- multi_panel_figure(
  width=6.2, height=4.2, unit="in",
  columns = 2, rows = 2)

#figure

#pav temp pca
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_pav_Temp.pdf",
  column = 1,
  row = 1,
  scaling = "none")

#pav temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PAV_Temp.pdf",
  column = 2,
  row = 1,
  scaling = "none")

#posv temp pca
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_posv_Temp.pdf",
  column = 1,
  row = 2,
  scaling = "none")

#posv temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PosV_Temp.pdf",
  column = 2,
  row = 2,
  scaling = "none")

##pav prec pca
#figure %<>% fill_panel(
#  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_pav_Precip.pdf",
#  column = 1,
#  row = 3,
#  scaling = "none")

##pav prec violin
#figure %<>% fill_panel(
#  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PAV_Precip.pdf",
#  column = 2,
#  row = 3,
#  scaling = "none")

##posv prec pca
#figure %<>% fill_panel(
#  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_posv_Precip.pdf",
#  column = 1,
#  row = 4,
#  scaling = "none")

#posv prec violin
#figure %<>% fill_panel(
#  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PosV_Precip.pdf",
#  column = 2,
#  row = 4,
#  scaling = "none")

pdf(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//fig3.pdf", height = 4.2, width = 6.2)
  figure
  dev.off()
png(filename = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//fig3.png", height = 4.2, width = 6.2, units = "in", res = 300)
  figure
  dev.off()

#pdf(file = paste0(bioclim_dir,"/pca_violin_pav_posv_prec.pdf"))
#  grid.arrange(pca_pav_prec,violin_pav_prec,
#               pca_posv_prec,violin_posv_prec,ncol = 2)
#  dev.off()
```

Use SNP PCA instead of posv

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)
library(ggrepel)

bioclim_dir = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/"
bioclim_pca = read.table(file = paste0(bioclim_dir,"/bioclim_pca.txt"),header = T,sep = "\t")

#add snp pc values
snp_df = read.table(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/01_snp_pca/snp_pca.txt", sep = "\t")
snp_df = snp_df[,c(1,2,30)]
colnames(snp_df) = c("PC1_snp","PC2_snp","Common_Name")

for (i in 1:nrow(snp_df)) {
  add_df = bioclim_pca[which(bioclim_pca$Common_Name == snp_df$Common_Name[i]),]
  add_vect = add_df[1,]
  add_vect$Tag = "SNP"
  add_vect$PC1 = snp_df[i,1]
  add_vect$PC2 = snp_df[i,2]
  bioclim_pca = rbind(bioclim_pca,add_vect)
}

#tidy
bioclim_pca_tidy = bioclim_pca %>% 
  gather(key = "Variable",value = "Value",3:21)

pca_snp_tmp = pca_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "SNP",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = T,code = "C")
violin_snp_tmp = violin_bioclim_plot(df = bioclim_pca_tidy, dir = bioclim_dir,tag = "SNP",unit_adj_function = div_ten,units = '\u00b0C',variable = "Temp",save = T, PC1_cutoff_upper = -25, PC2_cutoff_lower = -100)

#pca_snp_tmp
#violin_snp_tmp


```

```{r}
library(multipanelfigure)

height_fig = 6.4
width_fig = 6.2

figure <- multi_panel_figure(
  width=width_fig, height=height_fig, unit="in",
  columns = 2, rows = 3)

#figure

#pav temp pca
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_pav_Temp.pdf",
  column = 1,
  row = 1,
  scaling = "none")

#pav temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PAV_Temp.pdf",
  column = 2,
  row = 1,
  scaling = "none")

#posv temp pca
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_posv_Temp.pdf",
  column = 1,
  row = 2,
  scaling = "none")

#posv temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_PosV_Temp.pdf",
  column = 2,
  row = 2,
  scaling = "none")

#snp temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/pca_SNP_Temp.pdf",
  column = 1,
  row = 3,
  scaling = "none")

#snp temp violin
figure %<>% fill_panel(
  "/Users/alanyocca/Documents/01_athal_cns/29_bioclim/violin_SNP_Temp.pdf",
  column = 2,
  row = 3,
  scaling = "none")


###


pdf(file = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//fig3_snp.pdf", height = height_fig, width = width_fig)
  figure
  dev.off()
png(filename = "/Users/alanyocca/Documents/01_athal_cns/29_bioclim//fig3_snp.png", height = height_fig, width = width_fig, units = "in", res = 300)
  figure
  dev.off()
```



