---
title: "Athal_PCA"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Athal_PCA

principle components analysis on cns presence absence / transposed stuff

Example matrix making with variable genes:

```{r}
rm(list=ls(all=TRUE))
library(tidyverse)
library(ggplot2)

suffix <- "_var.txt"
path = "/Users/alanyocca/Documents/01_athal_cns/02_GO/01_data/gene_calls/"
list_of_files <- dir(path, pattern=paste0("SRR.*",suffix), full.names = T)

#remove Col-0, otherwise PCA plot split in one direction since variation incredibly low by comparison
#nevermind, col-0 not the problem, this one is
list_of_files <- list_of_files[! grepl("6036",list_of_files)]

accession_list <- gsub(paste0(path,"/*"),'',list_of_files) %>%
  gsub(suffix,'',.)
loaded_list_of_files <- lapply(list_of_files,function(i){
  scan(file = i,what = character())
})
for (i in 1:length(accession_list)) {
  names(loaded_list_of_files)[i] <- accession_list[i]
}
#View(names(loaded_list_of_files))

out <- t(splitstackshape:::charMat(listOfValues = loaded_list_of_files, fill = 0L))
colnames(out) <- accession_list
out_moved <- as.data.frame(out)
write.table(out_moved,file = paste0(path,"/pca_matrix",suffix), sep = "\t", quote = F)
```


just see if CNS cluster by admixture groups, geography, or nothing
think about finding geographic info / admixture groups later, now just try and get pca to run

```{r}
#?prcomp()
#have cns presence absence / transposed matricies from: athal_cns_upsetr.Rmd
#####only contains variable CNS
cns_missing <- read.table(file =  "/Users/alanyocca/Documents/01_athal_cns/cns_calls/acc_missing/01_final/01_single_rep/acc_cns_matrix_missing.txt", sep = "\t", header = T)
cns_moved <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/cns_calls/acc_moved/01_final/01_single_rep/acc_cns_matrix_moved.txt", sep = "\t", header = T)
gene_var <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/02_GO/01_data/gene_calls/pca_matrix_var.txt", sep = "\t", header = T)
#later, combine them, but give different value? differentiate? eh maybe keep them as 1 or 0..
#need transposed for prcomp: feature as columns, accession as rows
cns_missing_trans <- t(cns_missing)
rownames(cns_missing_trans) <- colnames(cns_missing)
cns_moved_trans <- t(cns_moved)
rownames(cns_moved_trans) <- colnames(cns_moved)
gene_var_trans <- t(gene_var)
rownames(gene_var_trans) <- colnames(gene_var)

#add another column that list geographic location... bin into categories...
#add another column that lists admixture group

group_assignment <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/final_genome_eco_id.txt", sep = "\t", header = T, row.names = NULL)
#best way to add these...
#View(rownames(cns_missing_trans))
#make column with SRR then, subset group_assignment, then merge... should work.. might as well not even subset
#going to be a little hacky:

cns_missing_trans_grp <- cbind(cns_missing_trans, read.table(text = row.names(cns_missing_trans), sep = "_", header = F, stringsAsFactors = F, fill = T))
first_srr_col <- ncol(cns_missing_trans)+1
colnames(cns_missing_trans_grp)[first_srr_col] <- "SRR"
#?cbind
cns_missing_trans_grp <- merge(cns_missing_trans_grp,group_assignment, by.x = 'SRR')

cns_moved_trans_grp <- cbind(cns_moved_trans, read.table(text = row.names(cns_moved_trans), sep = "_", header = F, stringsAsFactors = F, fill = T))
first_srr_col <- ncol(cns_moved_trans)+1
colnames(cns_moved_trans_grp)[first_srr_col] <- "SRR"
#?cbind
cns_moved_trans_grp <- merge(cns_moved_trans_grp,group_assignment, by.x = 'SRR')

gene_var_trans_grp <- cbind(gene_var_trans, read.table(text = row.names(gene_var_trans), sep = "_", header = F, stringsAsFactors = F, fill = T))
first_srr_col <- ncol(gene_var_trans)+1
colnames(gene_var_trans_grp)[first_srr_col] <- "SRR"
#?cbind
gene_var_trans_grp <- merge(gene_var_trans_grp,group_assignment, by.x = 'SRR')

cns_var <- rbind(cns_moved, cns_missing)
cns_var_trans <- t(cns_var)
rownames(cns_var_trans) <- colnames(cns_var)
cns_var_trans_grp <- cbind(cns_var_trans, read.table(text = row.names(cns_var_trans), sep = "_", header = F, stringsAsFactors = F, fill = T))
first_srr_col <- ncol(cns_var_trans)+1
colnames(cns_var_trans_grp)[first_srr_col] <- "SRR"
#?cbind
cns_var_trans_grp <- merge(cns_var_trans_grp,group_assignment, by.x = 'SRR')



#new one,
#row accessions
#one column for latitude, one for longitude
#hmmmm maybe use that thing saw on twitter to make graph morphing from one position to another..
#would need to figure out 2d coordinates though shouldn't be too hard
SraRunTable <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/SraRunTable.txt", header = T, row.names = NULL, sep = "\t")
#interested in Sample_Name
#and Run.. take from above:
SRR_list <- gsub("_.*","",colnames(cns_missing))
names(SRR_list) <- colnames(cns_missing)
SraRunTable_srr <- SraRunTable[SraRunTable$Run %in% SRR_list,]
SraRunTable_short <- SraRunTable_srr[,c("Run", "ecotype")]
eco_table <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/query.csv", header = T, row.names = NULL, sep = ",")
eco_table_srr <- eco_table[eco_table$tg_ecotypeid %in% SraRunTable_short$ecotype,]
colnames(eco_table_srr)[1] <- "ecotype"
srr_eco_table <- merge(eco_table_srr,SraRunTable_short,by.x = "ecotype")
run_lat_long <- srr_eco_table[,c("Run","latitude","longitude")]
lat_long_pca_table <- run_lat_long[,c("latitude","longitude")]
rownames(lat_long_pca_table) <- names(SRR_list)

#View(lat_long_pca_table)
library("stats")
#?prcomp

#need to remove constant columns:
#which(apply(cns_moved_trans_grp[,2:4802], 2, var)==0)
#const 
#1 
cns_moved_trans_grp[,2:4802] <- cns_moved_trans_grp[,2:4802][ , apply(cns_moved_trans_grp[,2:4802], 2, var) != 0]

#View(gene_var_trans_grp[,5580:5593])
#View(gene_var_trans_grp[,1:10])
#which(apply(gene_var_trans_grp[,2:5593], 2, var)==0)
#lets automate this shit
gene_var_up_to <- nrow(gene_var) + 1
gene_var_trans_grp[,2:gene_var_up_to] <- gene_var_trans_grp[,2:gene_var_up_to][ , apply(gene_var_trans_grp[,2:gene_var_up_to], 2, var) != 0]

#combine missing and moved data....
mi_mo <- merge(cns_moved_trans_grp, cns_missing_trans_grp, by = "SRR")
mi_mo <- mi_mo[,-c(4803:4811)]

#cns_missing_pca <- prcomp(cns_missing_trans_grp[,2:1525], scale. = T)
#cns_moved_pca <- prcomp(cns_moved_trans_grp[,2:4802], scale. = T)
lat_long_pca <- prcomp(lat_long_pca_table)
#>95 of variance explained after:
#missing: PC26
#moved: PC27
#rerun with these
cns_missing_pca <- prcomp(cns_missing_trans_grp[,2:1525], rank. = 26)
cns_moved_pca <- prcomp(cns_moved_trans_grp[,2:4802], rank. = 26)
cns_var_pca <- prcomp(cns_var_trans_grp[,2:6326], rank. = 27)
gene_var_pca <- prcomp(gene_var_trans_grp[,2:gene_var_up_to], rank. = 26)
mi_mo_pca <- prcomp(mi_mo[,2:6326], rank. = 27)
#26 PCs to get > 95%
#summary(gene_var_pca)
#View(cns_var_trans_grp[1,6325:6335])
#summary(cns_var_pca)
#27 PCs
#tmp <- summary(mi_mo_pca)
#tmp$importance[,1][2]
#27 PCs
###############################

#View(mi_mo[,c(6325:6335)])
#View(mi_mo[,c(4800:4815)])
#mi_mo[,c(2:6335)] <- sapply(mi_mo[,c(2:6335)],as.numeric)
#tmp <- sapply(mi_mo,class)
#View(tmp[6330:6344])  
  
#install.packages("ggfortify")
library("ggplot2")
library("ggfortify")

autoplot(cns_missing_pca, data = cns_missing_trans_grp, colour = "Group")
autoplot(cns_moved_pca, data = cns_moved_trans_grp, colour = "Group")
autoplot(lat_long_pca,data = lat_long_pca_df, colour = "Group")
autoplot(cns_var_pca,data = cns_var_trans_grp,colour = "Group")
autoplot(gene_var_pca,data = gene_var_trans_grp,colour = "Group")
autoplot(mi_mo_pca,data = mi_mo, colour = "Group.y")

png(filename = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_posv_pca.png")
  autoplot(mi_mo_pca,data = mi_mo, colour = "Group.y")
  dev.off()
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_posv_pca.pdf")
  autoplot(mi_mo_pca,data = mi_mo, colour = "Group.y")
  dev.off()
#hmm it wasn't col-0 fault, I bet it was SRR1946036 something like that
#View(gene_var_trans_grp$SRR)
#not super clustered but PC1 explains most of variation, lawdy let it be latitude

cns_missing_pca_df <- as.data.frame(cns_missing_pca$x)
cns_missing_pca_df$Group <- cns_missing_trans_grp$Group
cns_missing_pca_df$Tag <- rep("Missing",nrow(cns_missing_pca_df))
cns_missing_pca_df$Accession <- colnames(cns_missing)

cns_moved_pca_df <- as.data.frame(cns_moved_pca$x)
cns_moved_pca_df$Group <- cns_moved_trans_grp$Group
cns_moved_pca_df$Accession <- colnames(cns_moved)
cns_moved_pca_df$Tag <- rep("Moved",nrow(cns_moved_pca_df))

gene_var_pca_df <- as.data.frame(gene_var_pca$x)
gene_var_pca_df$Group <- gene_var_trans_grp$Group
gene_var_pca_df$Accession <- colnames(gene_var)
gene_var_pca_df$Tag <- rep("Gene_var",nrow(gene_var_pca_df))

mi_mo_pca_df <- as.data.frame(mi_mo_pca$x)
mi_mo_pca_df$Group <- mi_mo$Group.y
mi_mo_pca_df$Accession <- colnames(cns_moved)
mi_mo_pca_df$Tag <- rep ("Mi_Mo",nrow(mi_mo_pca_df))

lat_long_pca_df <- as.data.frame(lat_long_pca$x)
lat_long_pca_df$Accession <- rownames(lat_long_pca_table)
#get the right groups...
group_lat_long <- as.vector(rownames(lat_long_pca_table))
srr <- gsub("_.*", "", group_lat_long)
genome_srr <- data.frame(SRR = srr,
                         Genome = as.vector(rownames(lat_long_pca_table)))
genome_group <- merge(genome_srr, group_assignment)
genome_group$Group <- unlist(genome_group$Group)
lat_long_pca_df$Group <- rep("",nrow(lat_long_pca_df))
for (i in 1:nrow(lat_long_pca_df)) {
  lat_long_pca_df$Group[i] <- as.vector(genome_group[which(genome_group$Genome == rownames(lat_long_pca_df)[i]),which(colnames(genome_group) == "Group")])
  #i <- 1
  #which(genome_group$Genome == rownames(lat_long_pca_df)[i])
  #as.vector(genome_group[1,5])
}
lat_long_pca_df$Tag <- rep("Geo",nrow(lat_long_pca_df))

#combine these... add another tag
missing_sub <- cns_missing_pca_df[,c("PC1","PC2","Group","Tag", "Accession")]
moved_sub <- cns_moved_pca_df[,c("PC1","PC2","Group","Tag", "Accession")]
gene_sub <- gene_var_pca_df[,c("PC1","PC2","Group","Tag", "Accession")]
#add trouble accession back in... try as NA first
#nope, put as 1,1 think thats out of bounds anyway
#colnames(gene_sub)
#problem_accession <- c(1,1,"germany","Gene_var","SRR1946036_bwa_alt_3_pbj_5_rename")
#actually only worked not doing this?
#well got an error message think might have been able to fix, but looks like its working just dropping this from this df
#gene_sub <- rbind(gene_sub,problem_accession)

merged_df <- rbind(missing_sub,gene_sub,moved_sub,lat_long_pca_df)
```

save merged_df
```{r}
write.table(merged_df, file = "/Users/alanyocca/Documents/01_athal_cns/pca_data_table.txt",quote = F,row.names = F,sep = "\t")
```

Depends on getting merged_df object from above code block
UPDATE: can stand alone now since saved merged_df
```{r}

library("transformr")
library("gganimate")
library(tidyverse)

merged_df = read.table( file = "/Users/alanyocca/Documents/01_athal_cns/pca_data_table.txt",row.names = NULL,sep = "\t", header = T)

#just geo to missing
#flip y coords.. for missing
geo_to_missing_df <- merged_df[merged_df$Tag == "Missing" | merged_df$Tag == "Geo",]
geo_to_missing_df[geo_to_missing_df$Tag == "Missing","PC2"] <- -1 * geo_to_missing_df[geo_to_missing_df$Tag == "Missing","PC2"]
geo_to_missing <- ggplot(geo_to_missing_df, aes(PC1, PC2)) +
  geom_point(aes(colour = factor(Group))) +
  labs(title="state: {closest_state}") +
  transition_states(Tag)
geo_to_missing
anim_save("/Users/alanyocca/Documents/01_athal_cns/geo_to_missing_pca.gif", geo_to_missing)

#missing to moved
library(ggrepel)

moved_to_missing <- merged_df[merged_df$Tag == "Missing" | merged_df$Tag == "Moved",]
moved_to_missing$Tag <- gsub("Missing", "PAV", moved_to_missing$Tag) 
moved_to_missing$Tag <- gsub("Moved", "PosV", moved_to_missing$Tag)
moved_to_missing_plot <- ggplot(moved_to_missing, aes(PC2, PC1)) +
  geom_point(aes(colour = Group)) +
  labs(fill="Admixture Group") +
  labs(title="state: {closest_state}") +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  geom_text(label=moved_to_missing$Accession) +
  transition_states(Tag)
animate(moved_to_missing_plot, width = 800, height = 450)

anim_save("/Users/alanyocca/Documents/01_athal_cns/moved_to_missing_pca.gif", moved_to_missing_plot, width = 776, height = 563)

library(scales)
show_col(hue_pal()(4))
#fuck with colors later to get density distribution consistent with other plots
#consider theme = minimal for this....



##
mi_mo_pca_summary <- summary(mi_mo_pca)
#mi_mo_pca_summary$importance[,1][2]
mi_mo_graph <- mi_mo_pca_df %>%
  ggplot(aes(x = PC1,y = PC2, colour = Group)) +
  geom_point() +
  xlab(label = paste0("PC1 (",mi_mo_pca_summary$importance[,1][2],"%)")) +
  ylab(label = paste0("PC1 (",mi_mo_pca_summary$importance[,1][3],"%)")) +
  ggtitle("PCA PAV and PosV")
mi_mo_graph
#
#pdf(file = "/Users/alanyocca/Documents/01_athal_cns/cns_calls/mi_mo_pca.pdf", width = 12, height = 6)
#  plot(mi_mo_graph)
#  dev.off()

#geo to moved
geo_to_moved <- ggplot(merged_df[merged_df$Tag == "Moved" | merged_df$Tag == "Geo",], aes(PC1, PC2)) +
  geom_point(aes(colour = factor(Group))) +
  labs(title="state: {closest_state}") +
  transition_states(Tag)
geo_to_moved
anim_save("/Users/alanyocca/Documents/01_athal_cns/geo_to_moved_pca.gif", geo_to_moved)


#flip gene var axes
#merged_df <- rbind(missing_sub,gene_sub,moved_sub,lat_long_pca_df)
merged_df[merged_df$Type == "Gene_var",c("PC2")] <- merged_df[merged_df$Type == "Gene_var",c("PC2")] * -1

anim <- ggplot(merged_df, aes(PC1, PC2)) +
  geom_point(aes(colour = factor(Group))) +
  xlim(-10,15) +
  ylim(-20,20) +
  labs(title="state: {closest_state}") +
  transition_states(Tag)
anim
anim_save("/Users/alanyocca/Documents/01_athal_cns/gene_to_geo_to_moved_to_missing_pca.gif", anim)

#p <- ggplot(data = cns_missing_pca_df, aes(x = PC1, y = PC2, colour = Group)) + 
#    geom_point(size=2) + 
#   # scale_fill_hue(l=40) + 
#    coord_fixed(ratio=1, xlim=range(cns_missing_pca_df$PC1), ylim=range(cns_missing_pca_df$PC2)) 
#p
#?read.table
?readChar
summary(cns_missing_pca)
summary(cns_moved_pca)
summary(lat_long_pca)
sd(lat_long_pca_table$latitude)
sd(lat_long_pca_table$longitude)


#save these plots for later
#save the data frames also?
#no so long as things don't move, were really quick to make

png(filename = "/Users/alanyocca/Documents/01_athal_cns/cns_calls/acc_missing/01_final/01_single_rep/pca_plot_missing.png")
  plot(autoplot(cns_missing_pca, data = cns_missing_trans_grp, colour = "Group"))
  dev.off()

png(filename = "/Users/alanyocca/Documents/01_athal_cns/cns_calls/acc_moved/01_final/01_single_rep/pca_plot_moved.png")
  plot(autoplot(cns_moved_pca, data = cns_moved_trans_grp, colour = "Group"))
  dev.off()

  
ggplot(airq, aes(Day, Temp, group = Month)) + 
  geom_line() + 
  geom_segment(aes(xend = 31, yend = Temp), linetype = 2, colour = 'grey') + 
  geom_point(size = 2) + 
  geom_text(aes(x = 31.1, label = Month), hjust = 0) + 
  transition_reveal(Day) + 
  coord_cartesian(clip = 'off') + 
  labs(title = 'Temperature in New York', y = 'Temperature (°F)') + 
  theme_minimal() + 
  theme(plot.margin = margin(5.5, 40, 5.5, 5.5))
  
geo_to_missing <- ggplot(geo_to_missing_df, aes(PC1, PC2, group = Group)) +
  geom_line() +
  geom_segment(aes(xend = PC1, yend = PC2), linetype = 2) +
  geom_point() +
  labs(title="state: {closest_state}") +
  transition_reveal(Tag)
geo_to_missing

#devtools::install_github("thomasp85/transformr")
library("transformr")

geo_to_missing <- ggplot(geo_to_missing_df, aes(PC1, PC2)) +
  geom_segment(xend = )
?transition_reveal
geo_to_missing
lapply(geo_to_missing_df, class)
#hmm just convert missing, moved, geo to a numeric?
#Geo, Missing, Moved
#1,   2,        3
geo_to_missing_df$Tag_num <- rep(0,nrow(geo_to_missing_df))
for (i in 1:nrow(geo_to_missing_df)) {
  if (geo_to_missing_df$Tag[i] == "Geo") {
    geo_to_missing_df$Tag_num[i] <- 1
  } else if (geo_to_missing_df$Tag[i] == "Missing") {
    geo_to_missing_df$Tag_num[i] <- 2
  } else if (geo_to_missing_df$Tag[i] == "Moved") {
    geo_to_missing_df$Tag_num[i] <- 3
  }
}
library(tidyverse)
#rbind(missing_sub,moved_sub,lat_long_pca_df)
line_seg_df <- cbind(lat_long_pca_df,missing_sub)
colnames(line_seg_df)
line_seg_col_name <- c("PC1.1","PC2.1","Accession","Group","Tag","PC1.2","PC2.2","Group","Tag","Accession")
colnames(line_seg_df) <- line_seg_col_name
line_seg_df <- line_seg_df[,c(1,2,6,7)]

line_seg_graph <- line_seg_df %>%
  ggplot(aes(PC1.2,PC2.2)) +
  geom_segment(aes(xend = PC1.1, yend = PC2.1), arrow = arrow())
line_seg_graph
  
  ggplot(seals, aes(long, lat)) +
  geom_segment(aes(xend = long + delta_long, yend = lat + delta_lat),
    arrow = arrow(length = unit(0.1,"cm"))) +

#I think it might be better for this part to just manually do a line graph from one dot to the next
#data need morphed?
#hmm

```


Depends on getting merged_df object from two blocks above:
Messing around with formatting
```{r}
#rm(list=ls(all=TRUE))
library("transformr")
library("gganimate")
#missing to moved
library(ggrepel)

merged_df <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/pca_data_table.txt",sep = "\t",row.names = NULL, header = T)

moved_to_missing <- merged_df[merged_df$Tag == "Missing" | merged_df$Tag == "Moved",]
moved_to_missing$Tag <- gsub("Missing", "PAV", moved_to_missing$Tag) 
moved_to_missing$Tag <- gsub("Moved", "PosV", moved_to_missing$Tag)
moved_to_missing$Accession <- as.character(moved_to_missing$Accession)

#translate to common names
info_table <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/final_gen_eco_cn_id.txt",sep = "\t",row.names = NULL,header = T)
#easiest way to switch out names....
#i <- 1
cn_vect <- c()

for (i in 1:nrow(moved_to_missing)) {
  srr_split <- unlist(strsplit(moved_to_missing$Accession[i], split = "_"))
  cn_index <- which(grepl(srr_split[1],info_table$SRR))
  common_name <- as.character(info_table$Common_Name[cn_index])
  cn_vect <- c(cn_vect,common_name)
}
moved_to_missing <- cbind(moved_to_missing, cn_vect)

moved_to_missing_plot <- ggplot(moved_to_missing, aes(PC2, PC1)) +
  geom_point(aes(colour = Group), size = 3) +
  theme(legend.text=element_text(size=25),
        legend.title = element_text(size = 25),
        axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25)) +
  labs(fill="Admixture Group") +
  #theme(legend.text=element_text(size=50)) +
  labs(title="state: {closest_state}") +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  #ggrepel::geom_text_repel(label=moved_to_missing$cn_vect, box.padding = unit(3, 'lines')) +
  transition_states(Tag)
animate(moved_to_missing_plot, width = 800, height = 450)
#?animate()

anim_save("/Users/alanyocca/Documents/01_athal_cns/moved_to_missing_pca_50.gif", moved_to_missing_plot, units = "in", width = (7.76*2), height = (5.63*2), res = 100)
dev.off()
#hmmm other thing I can think is get the position of static spread out and layer those on moving graph...
library(scales)
show_col(hue_pal()(4))
#fuck with colors later to get density distribution consistent with other plots
#consider theme = minimal for this....

```



```{r}
#jitter plot

plot <- plotdat %>% ggplot(aes(x=decile,y=count,color=color)) +
  geom_point(position = position_jitter(width = 0.2, height = 0.2), size=2) +
  scale_color_viridis_d() +
  scale_x_continuous(breaks=1:10, minor_breaks = seq(0.5,10.5,1)) +
  theme_ms() + theme(legend.position = "none", axis.text.y = element_blank(), axis.title.x = element_text(hjust=0), panel.grid.minor.x = element_line(size=0.3,color="gray"), panel.grid.major = element_blank(), plot.caption = element_text(size=10)) +
  labs(x=expression("Net wealth decile (poor" %->% "rich)"), y="", title="Rich people think they are middle class", subtitle ="Actual and estimated position in the net wealth distribution in Austria", caption="Data: HFCS 2014, OeNB. Figure: @matschnetzer") +
  geom_label(aes(x=10,y=1.3,label=label,hjust=0.8),color=msc_palette[1],data=labdf, size=4) +
  transition_states(state,
                    transition_length = 15,
                    state_length = 20)

#install.packages("devtools")
#library("devtools")
#update.packages("ggplot2")
#library("ggplot2")
#sessionInfo()
#devtools::install_github('thomasp85/gganimate')
library(gganimate)
#install.packages("gifski")
library(gifski)

mtcars
ggplot(mtcars, aes(x = am, y = vs)) + geom_point(position = "jitter")
ggplot(mtcars, aes(x = am, y = vs)) + geom_point(position = position_jitter(w = 0.1, h = 0.1))
ggplot(mtcars, aes(x = am, y = vs)) +
  geom_point()

anim <- animate(plot, height=4, width=8, nframes = 100, res=300, unit = "in")
anim_save("hfcs.gif", anim)

airq <- airquality
airq$Month <- format(ISOdate(2004,1:12,1),"%B")[airq$Month]

View(airquality)
anim <- ggplot(airquality, aes(Day, Temp)) +
  geom_point(aes(colour = factor(Month))) +
  transition_states(Day)
anim

#try subsetting to just two days and see if can get for to work
test_anim <- airquality[airquality$Day %in% c(1,25),]
anim <- ggplot(test_anim, aes(Day, Temp)) +
  geom_point(aes(colour = factor(Month))) +
  transition_states(Day)
anim
#Nice! That worked!!

#data frame
#tidy
#accession, X coord, Y coord, State


```


MCA instead of PCA:

```{r}

install.packages(c("FactoMineR", "factoextra"))
library("FactoMineR")
library("factoextra")

#a few objects to take from above code
#cns_var_trans_grp
#cns_missing_trans_grp
#cns_moved_trans_grp
#lat_long_pca_table
#cns_missing_pca <- prcomp(cns_missing_trans_grp[,2:1525], rank. = 26)
#cns_moved_pca <- prcomp(cns_moved_trans_grp[,2:4802], rank. = 26)
#cns_var_pca <- prcomp(cns_var_trans_grp[,2:6326], rank. = 27)

#res.mca <- MCA(poison.active, graph = FALSE)
#convert to factor
cns_missing_trans_grp[,2:1525] <- as.factor(cns_missing_trans_grp[,2:1525])
res.missing <- MCA(cns_missing_trans_grp[,2:1525], graph = F)
#?MCA
#fviz_screeplot(res.missing, addlabels = TRUE)
fviz_mca_biplot(res.missing, 
               repel = TRUE, # Avoid text overlapping (slow if many point)
               ggtheme = theme_minimal())




```


#make some normal distributions for presentation, high resolution
```{r}
#
library(tidyverse)
library(ggplot2)

#make normal distribution dataframe
test_seq <- seq(-5, 5, by = .01)
test_df <- data.frame(X = test_seq,
                      Prob = dnorm(test_seq))
#
test_dist <- test_df %>%
  ggplot(aes(x = X, y = Prob)) +
  geom_point() +
 # theme(axis.title.y = element_blank()) +
  theme_void()
test_dist
#

png(filename = "/Users/alanyocca/Documents/01_athal_cns/normal_dist.png",width = 5.21, height = 2.47, res = 600, units = "in")
  plot(test_dist)
  dev.off()
```

Work on Figures for manuscript, static missing and moved plots with same axes, same spline lines, and labeled points

```{r}
#rm(list=ls(all=TRUE))
library(ggplot2)
library(tidyverse)
library(ggrepel)

merged_df = read.table( file = "/Users/alanyocca/Documents/01_athal_cns/pca_data_table.txt",row.names = NULL,sep = "\t", header = T)

moved_to_missing <- merged_df[merged_df$Tag == "Missing" | merged_df$Tag == "Moved",]
moved_to_missing$Tag <- gsub("Missing", "PAV", moved_to_missing$Tag) 
moved_to_missing$Tag <- gsub("Moved", "PosV", moved_to_missing$Tag)
moved_to_missing$Accession = as.character(moved_to_missing$Accession)

#translate to common names
info_table <- read.table(file = "/Users/alanyocca/Documents/01_athal_cns/final_gen_eco_cn_id.txt",sep = "\t",row.names = NULL,header = T)
#easiest way to switch out names....
#i <- 1
cn_vect <- c()

for (i in 1:nrow(moved_to_missing)) {
  srr_split <- unlist(strsplit(moved_to_missing$Accession[i], split = "_"))
  cn_index <- which(grepl(srr_split[1],info_table$SRR))
  common_name <- as.character(info_table$Common_Name[cn_index])
  cn_vect <- c(cn_vect,common_name)
}
moved_to_missing <- cbind(moved_to_missing, cn_vect)
colnames(moved_to_missing)[6] = "Common_name"

#check line crossing
moved_to_missing = moved_to_missing %>% 
  mutate(Above = ifelse(PC1 > (4*PC2), "True", "False"))
#hmm checking switching is a little more tricky... need to align those with different tags, merge first? eh make a separate df, do in a loop yourself
cross_df = data.frame(cn_vect = character(),
                      cross = character())
#i = 2
for ( i in 1:length(unique(cn_vect))) {
  loop_df = moved_to_missing[which(grepl(cn_vect[i],moved_to_missing$Common_name)),]
  cross = ifelse(loop_df[1,"Above"] == loop_df[2,"Above"],"False","True")
  loop_cross = c(cn_vect[i],cross)
  cross_df = rbind(cross_df,loop_cross)
  colnames(cross_df) = c("Common_name","cross")
  cross_df$Common_name = as.character(cross_df$Common_name)
  cross_df$cross = as.character(cross_df$cross)
  rm(loop_df,cross,loop_cross)
}
#nrow(cross_df[which(grepl("True",cross_df$cross)),])
#10 / 30 cross the spline

#best way to highlight for labeling, add another column, only gets label if crosses
moved_to_missing = merge(moved_to_missing,cross_df)
#

#only label those that cross
moved_to_missing$Label <- ""
moved_to_missing$Common_name = as.character(moved_to_missing$Common_name)
for (i in 1:nrow(moved_to_missing)){
  if (moved_to_missing$cross[i] == "True") {
    moved_to_missing$Label[i] = moved_to_missing$Common_name[i]
  }
}

pav_pca = moved_to_missing[which(grepl("PAV",moved_to_missing$Tag)),]
PAV_plot <- pav_pca %>% 
  ggplot(aes(x = PC2, y = PC1, label = Label)) +
  geom_point(aes(colour = Group), size = 3) +
  ylim(-10,22) +
  xlim(-14,14) +
  geom_abline(intercept = 0, slope = 4, color="red", size=1.5) +
#  theme(legend.text=element_text(size=25),
#        legend.title = element_text(size = 25),
#        axis.text=element_text(size=25),
#        axis.title.x = element_text(size=25),
#        axis.title.y = element_text(size=25),
#        title = element_text(size=25)) +
  labs(fill="Admixture Group") +
  #theme(legend.text=element_text(size=50)) +
  ggtitle(label="PAV") +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  ggrepel::geom_text_repel(box.padding = 3, size = 10) +
  theme_minimal() +
  theme(axis.text=element_text(size=25),
        axis.title.x = element_text(size=25),
        axis.title.y = element_text(size=25),
        title = element_text(size=25),
        legend.position = "none")
#hide legend because combining in inkscape with below
PAV_plot
#

#pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_plot.pdf", width = (7.76*2), height = (5.63*2))
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_plot.pdf")
  plot(PAV_plot)
  dev.off()
#
#fix Group names in here:
#same shit for pav
posv_pca = moved_to_missing[which(grepl("PosV",moved_to_missing$Tag)),]

posv_pca$Group = gsub("admixed","Admixed",posv_pca$Group)
posv_pca$Group = gsub("asia","Asia",posv_pca$Group)
posv_pca$Group = gsub("central_europe","Central Europe",posv_pca$Group)
posv_pca$Group = gsub("germany","Germany",posv_pca$Group)
posv_pca$Group = gsub("italy_balkan_caucasus","Italy Balkan Caucasus",posv_pca$Group)
posv_pca$Group = gsub("relic","Relic",posv_pca$Group)
posv_pca$Group = gsub("south_sweden","South Sweden",posv_pca$Group)
posv_pca$Group = gsub("spain","Spain",posv_pca$Group)
posv_pca$Group = gsub("western_europe","Western Europe",posv_pca$Group)

pav_pca$Group = gsub("admixed","Admixed",pav_pca$Group)
pav_pca$Group = gsub("asia","Asia",pav_pca$Group)
pav_pca$Group = gsub("central_europe","Central Europe",pav_pca$Group)
pav_pca$Group = gsub("germany","Germany",pav_pca$Group)
pav_pca$Group = gsub("italy_balkan_caucasus","Italy Balkan Caucasus",pav_pca$Group)
pav_pca$Group = gsub("relic","Relic",pav_pca$Group)
pav_pca$Group = gsub("south_sweden","South Sweden",pav_pca$Group)
pav_pca$Group = gsub("spain","Spain",pav_pca$Group)
pav_pca$Group = gsub("western_europe","Western Europe",pav_pca$Group)




#posv_pca = moved_to_missing[which(grepl("PosV",moved_to_missing$Tag)),]
PosV_plot <- posv_pca %>% 
  ggplot(aes(x = PC2, y = PC1, label = Label)) +
  geom_point(aes(colour = Group), size = 3) +
  ylim(-10,22) +
  xlim(-14,14) +
  geom_abline(intercept = 0, slope = 4, color="red", size=1.5) +
  labs(fill="Admixture Group") +
  #theme(legend.text=element_text(size=50)) +
  ggtitle(label="PosV") +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  ggrepel::geom_text_repel(box.padding = 3, size = 10) +
  theme_minimal() +
  theme(legend.text=element_text(size=25),
      legend.title = element_text(size = 25),
      axis.text=element_text(size=25),
      axis.title.x = element_text(size=25),
      axis.title.y = element_text(size=25),
      title = element_text(size=25),
      legend.position = "bottom") 
PosV_plot
#dev.off()

#pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/posv_plot.pdf", width = (7.76*2), height = (5.63*2))
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/posv_plot.pdf")
  plot(PosV_plot)
  dev.off()
#
#combine plots, fuck it ,, probs easier in illustrator
#give it one more go with facet_grid
pav_posv_pca = rbind(pav_pca,posv_pca)

pav_posv_plot <- pav_posv_pca %>% 
  ggplot(aes(x = PC2, y = PC1, label = Label)) +
  geom_point(aes(colour = Group), size = 3) +
  ylim(-10,22) +
  xlim(-14,14) +
  geom_abline(intercept = 0, slope = 4, color="red", size=1.5) +
  labs(fill="Admixture Group") +
  #theme(legend.text=element_text(size=50)) +
  #ggtitle(label=~Tag) +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  ggrepel::geom_text_repel(box.padding = 3, size = 7.5) +
  theme_minimal() +
  facet_wrap(~Tag) +
  theme(legend.text=element_text(size=20),
      legend.title = element_text(size = 20),
      axis.text=element_text(size=20),
      axis.title.x = element_text(size=20),
      axis.title.y = element_text(size=20),
      title = element_text(size=20),
      legend.position = "bottom",
      panel.spacing = unit(2, "lines"),
      strip.text = element_text(size=20)) 
pav_posv_plot
#dev.off()

#pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/posv_plot.pdf", width = (7.76*2), height = (5.63*2))
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_posv_plot.pdf", width = (7*2))
  plot(pav_posv_plot)
  dev.off()
#

#take labels off
#Decided left panel will be a and right will be b
pav_posv_pca$Tag = gsub("PAV","a.) PAV",pav_posv_pca$Tag)
pav_posv_pca$Tag = gsub("PosV","b.) PosV",pav_posv_pca$Tag)
pav_posv_plot_no_label <- pav_posv_pca %>% 
  ggplot(aes(x = PC2, y = PC1, label = Label)) +
  geom_point(aes(colour = Group), size = 3) +
  ylim(-10,22) +
  xlim(-14,14) +
  geom_abline(intercept = 0, slope = 4, color="red", size=1.5) +
  labs(fill="Admixture Group") +
  #theme(legend.text=element_text(size=50)) +
  #ggtitle(label=~Tag) +
  #ggrepel::geom_text_repel(label=moved_to_missing$Accession, point.padding = 2) +
  #ggrepel::geom_text_repel(box.padding = 3, size = 7.5) +
  theme_minimal() +
  facet_wrap(~Tag) +
  theme(legend.text=element_text(size=20),
      legend.title = element_text(size = 20),
      axis.text=element_text(size=20),
      axis.title.x = element_text(size=20),
      axis.title.y = element_text(size=20),
      title = element_text(size=20),
      legend.position = "bottom",
      panel.spacing = unit(2, "lines"),
      strip.text = element_text(size=20, hjust = 0)) 
pav_posv_plot_no_label
#dev.off()

#pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/posv_plot.pdf", width = (7.76*2), height = (5.63*2))
pdf(file = "/Users/alanyocca/Documents/01_athal_cns/25_PCA/pav_posv_plot_no_label.pdf", width = (7*2))
  plot(pav_posv_plot_no_label)
  dev.off()
#



#require(gridExtra)
library(gridExtra)

grid.arrange(PAV_plot, PosV_plot, ncol=2)
dev.off()

pdf(file = paste0(output_path,"_sushi_",chrom,"_",tair_chromstart,"_",tair_chromend,".pdf")
    ,width = (2.75*1.5), height = (1.5*2.125))
par(mfrow=c(4,1),mar=c(1,4,1,1))





#Figure out matching xy coords
#X
max(pav_pca$PC2)
#[1] 3.236182
max(posv_pca$PC2)
#[1] 13.48599

#Y
max(pav_pca$PC1)
#[1] 5.561055
max(posv_pca$PC1)
#[1] 21.51551

#X
min(pav_pca$PC2)
#[1] -13.37885
min(posv_pca$PC2)
#[1] -5.288059

#Y
min(pav_pca$PC1)
#[1] -9.614237
min(posv_pca$PC1)
#[1] -7.698688

#X = (-13.37885,13.48599) ~ (-14,14)
#Y = (-9.614237,21.51551) ~ (-10,22)

#try drawing line through points:
#PAV
#same as below could work
#PosV
#(-2.5,-10) & (0,0)
#slope:
#4
#y − y1 = m(x − x1)
#y + 10 = 4x + 10
#y = 4x

PAV_PosV_plot
#

#Think will just label points that cross the spline, figure out what the spline should be, then get vector of names for it


```















